\documentclass[12pt]{article}

\title{Volume 3 Portfolio Project Proposal}

\author{Zach Joachim\\Taylor Jones\\Trevor Wai\\Carson Watkin}

\begin{document}

\maketitle

\section{Project Description}

We plan to use time-series data to build an Autoregressive Integrated Moving Average (ARIMA) model to forecast 
the stock price and profits for The Coca-Cola Company. We want to forecast the sales volume of Coca-Cola products 
for the upcoming quarter, as well as years in the future to answer questions that will lead shareholders and 
leaders in the company to make informed decisions regarding production, distribution, and marketing strategies. 
With the analysis of sales volume trends, we want to anticipate market fluctuations and determine ways of 
optimizing resource allocation within Coca-Cola's many operations.

\section{Questions}

\begin{itemize}
    \item What will the sales volume for Sprite and Fanta be this quarter?
    \item Where will the stock price be at the end of the quarter? A Year? 5 Years?
    \item What will the profits of Diet Coke bring the company in 10 years?
    \item What drinks' sales volume will decrease and increase with the emergence of energy drinks?
    \item When will the stock price fall significantly next?
\end{itemize}

\section{Metrics}

\begin{itemize}
    \item Sales Volume of Coca-Cola products
    \item Profits
    \item Stock price
\end{itemize}

\section{Division of Work}

This is a very rough assignment of roles for this project, we will all be contributiing to many parts of this 
project. 
\begin{itemize}
    \item Zach Joachim $\Rightarrow$ Research and Document Organizer
    \item Taylor Jones $\Rightarrow$ Plotting and Analysis
    \item Trevor Wai $\Rightarrow$ Data Gathering and Cleaning
    \item Carson Watkin $\Rightarrow$ Modeling and Research
\end{itemize}

\end{document}